%Copyright 2014 Jean-Philippe Eisenbarth
%This program is free software: you can
%redistribute it and/or modify it under the terms of the GNU General Public
%License as published by the Free Software Foundation, either version 3 of the
%License, or (at your option) any later version.
%This program is distributed in the hope that it will be useful,but WITHOUT ANY
%WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A
%PARTICULAR PURPOSE. See the GNU General Public License for more details.
%You should have received a copy of the GNU General Public License along with
%this program.  If not, see <http://www.gnu.org/licenses/>.

%Based on the code of Yiannis Lazarides
%http://tex.stackexchange.com/questions/42602/software-requirements-specification-with-latex
%http://tex.stackexchange.com/users/963/yiannis-lazarides
%Also based on the template of Karl E. Wiegers
%http://www.se.rit.edu/~emad/teaching/slides/srs_template_sep14.pdf
%http://karlwiegers.com
\documentclass{scrreprt}
\synctex=1
\usepackage{listings}
\usepackage{underscore}
\usepackage[bookmarks=true, breaklinks=true]{hyperref}
\def\UrlBreaks{\do\/\do-}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\hypersetup{
    bookmarks=false,    % show bookmarks bar?
    pdftitle={Software Requirement Specification},    % title
    pdfauthor={Jean-Philippe Eisenbarth},                     % author
    pdfsubject={TeX and LaTeX},                        % subject of the document
    pdfkeywords={TeX, LaTeX, graphics, images}, % list of keywords
    colorlinks=true,       % false: boxed links; true: colored links
    linkcolor=blue,       % color of internal links
    citecolor=black,       % color of links to bibliography
    filecolor=black,        % color of file links
    urlcolor=purple,        % color of external links
    linktoc=page            % only page is linked
}%
\def\myversion{1.0 }
\date{}
%\title{%

%}
\usepackage{hyperref}
\begin{document}

\begin{flushright}
 \rule{16cm}{5pt}\vskip1cm
 \begin{bfseries}
  \Huge{SOFTWARE REQUIREMENTS\\ SPECIFICATION}\\
  \vspace{1.9cm}
  for\\
  \vspace{1.9cm}
  Traffic Light System\\
  \vspace{1.9cm}
  \LARGE{Version \myversion approved}\\
  \vspace{1.9cm}
  Prepared by 404 Team Name Not Found\\
  \vspace{1.9cm}
  HireMe Software Ltd.\\
  \vspace{1.9cm}
  \today\\
 \end{bfseries}
\end{flushright}

\tableofcontents


\chapter*{Revision History}

\begin{center}
 \begin{tabular}{|c|c|c|c|}
  \hline
  Name          & Date             & Reason For Changes & Version \\
  \hline
  Arun Woosaree & October 22, 2018 & Create document    & 1.0     \\
  % \hline
  % 31                      & 32     & 33                 & 34      \\
  \hline
 \end{tabular}
\end{center}

\chapter{Introduction}

\section{Purpose}
$<$Identify the product whose software requirements are specified in this
document, including the revision or release number. Describe the scope of the
product that is covered by this SRS, particularly if this SRS describes only
part of the system or a single subsystem.$>$

\section{Document Conventions}
$<$Describe any standards or typographical conventions that were followed when
writing this SRS, such as fonts or highlighting that have special significance.
For example, state whether priorities  for higher-level requirements are assumed
to be inherited by detailed requirements, or whether every requirement statement
is to have its own priority.$>$

\section{Intended Audience and Reading Suggestions}
$<$Describe the different types of reader that the document is intended for,
such as developers, project managers, marketing staff, users, testers, and
documentation writers. Describe what the rest of this SRS contains and how it is
organized. Suggest a sequence for reading the document, beginning with the
overview sections and proceeding through the sections that are most pertinent to
each reader type.$>$

\section{Project Scope}
$<$Provide a short description of the software being specified and its purpose,
including relevant benefits, objectives, and goals. Relate the software to
corporate goals or business strategies. If a separate vision and scope document
is available, refer to it rather than duplicating its contents here.$>$

\section{References}
$<$List any other documents or Web addresses to which this SRS refers. These may
include user interface style guides, contracts, standards, system requirements
specifications, use case documents, or a vision and scope document. Provide
enough information so that the reader could access a copy of each reference,
including title, author, version number, date, and source or location.$>$
\begin{enumerate}
 \item
       \textbf{Canada Transportation Act}:
       \url{https://www.otc-cta.gc.ca/eng/implementation-recent-amendments-canada-transportation-act}
\end{enumerate}


\chapter{Overall Description}

\section{Product Perspective}
$<$Describe the context and origin of the product being specified in this SRS.
For example, state whether this product is a follow-on member of a product
family, a replacement for certain existing systems, or a new, self-contained
product. If the SRS defines a component of a larger system, relate the
requirements of the larger system to the functionality of this software and
identify interfaces between the two. A simple diagram that shows the major
components of the overall system, subsystem interconnections, and external
interfaces can be helpful.$>$
In this SRS document, we are specifying the software for controlling the Traffic Light System (TLS) at a simple intersection. It is new self-contained software.

\section{Product Functions}
$<$Summarize the major functions the product must perform or must let the user
perform. Details will be provided in Section 3, so only a high level summary
(such as a bullet list) is needed here. Organize the functions to make them
understandable to any reader of the SRS. A picture of the major groups of
related requirements and how they relate, such as a top level data flow diagram
or object class diagram, is often effective.$>$

\section{User Classes and Characteristics}
$<$Identify the various user classes that you anticipate will use this product.
User classes may be differentiated based on frequency of use, subset of product
functions used, technical expertise, security or privilege levels, educational
level, or experience. Describe the pertinent characteristics of each user class.
Certain requirements may pertain only to certain user classes. Distinguish the
most important user classes for this product from those who are less important
to satisfy.$>$

\section{Operating Environment}
$<$Describe the environment in which the software will operate, including the
hardware platform, operating system and versions, and any other software
components or applications with which it must peacefully coexist.$>$

\section{Design and Implementation Constraints}
$<$Describe any items or issues that will limit the options available to the
developers. These might include: corporate or regulatory policies; hardware
limitations (timing requirements, memory requirements); interfaces to other
applications; specific technologies, tools, and databases to be used; parallel
operations; language requirements; communications protocols; security
considerations; design conventions or programming standards (for example, if the
customer’s organization will be responsible for maintaining the delivered
software).$>$

\section{User Documentation}
$<$List the user documentation components (such as user manuals, on-line help,
and tutorials) that will be delivered along with the software. Identify any
known user documentation delivery formats or standards.$>$
\section{Assumptions and Dependencies}

$<$List any assumed factors (as opposed to known facts) that could affect the
requirements stated in the SRS. These could include third-party or commercial
components that you plan to use, issues around the development or operating
environment, or constraints. The project could be affected if these assumptions
are incorrect, are not shared, or change. Also identify any dependencies the
project has on external factors, such as software components that you intend to
reuse from another project, unless they are already documented elsewhere (for
example, in the vision and scope document or the project plan).$>$


\chapter{External Interface Requirements}

\section{User Interfaces}
$<$Describe the logical characteristics of each interface between the software
product and the users. This may include sample screen images, any GUI standards
or product family style guides that are to be followed, screen layout
constraints, standard buttons and functions (e.g., help) that will appear on
every screen, keyboard shortcuts, error message display standards, and so on.
Define the software components for which a user interface is needed. Details of
the user interface design should be documented in a separate user interface
specification.$>$

\section{Hardware Interfaces}
$<$Describe the logical and physical characteristics of each interface between
the software product and the hardware components of the system. This may include
the supported device types, the nature of the data and control interactions
between the software and the hardware, and communication protocols to be
used.$>$

\section{Software Interfaces}
$<$Describe the connections between this product and other specific software
components (name and version), including databases, operating systems, tools,
libraries, and integrated commercial components. Identify the data items or
messages coming into the system and going out and describe the purpose of each.
Describe the services needed and the nature of communications. Refer to
documents that describe detailed application programming interface protocols.
Identify data that will be shared across software components. If the data
sharing mechanism must be implemented in a specific way (for example, use of a
global data area in a multitasking operating system), specify this as an
implementation constraint.$>$

\section{Communications Interfaces}
$<$Describe the requirements associated with any communications functions
required by this product, including e-mail, web browser, network server
communications protocols, electronic forms, and so on. Define any pertinent
message formatting. Identify any communication standards that will be used, such
as FTP or HTTP. Specify any communication security or encryption issues, data
transfer rates, and synchronization mechanisms.$>$


\chapter{System Features}
$<$This template illustrates organizing the functional requirements for the
product by system features, the major services provided by the product. You may
prefer to organize this section by use case, mode of operation, user class,
object class, functional hierarchy, or combinations of these, whatever makes the
most logical sense for your product.$>$

\section{System Feature 1}
$<$Don’t really say “System Feature 1.” State the feature name in just a few
words.$>$

\subsection{Description and Priority}
$<$Provide a short description of the feature and indicate whether it is of
High, Medium, or Low priority. You could also include specific priority
component ratings, such as benefit, penalty, cost, and risk (each rated on a
relative scale from a low of 1 to a high of 9).$>$

\subsection{Stimulus/Response Sequences}
$<$List the sequences of user actions and system responses that stimulate the
behavior defined for this feature. These will correspond to the dialog elements
associated with use cases.$>$

\subsection{Functional Requirements}
$<$Itemize the detailed functional requirements associated with this feature.
These are the software capabilities that must be present in order for the user
to carry out the services provided by the feature, or to execute the use case.
Include how the product should respond to anticipated error conditions or
invalid inputs. Requirements should be concise, complete, unambiguous,
verifiable, and necessary. Use “TBD” as a placeholder to indicate when necessary
information is not yet available.$>$

$<$Each requirement should be uniquely identified with a sequence number or a
meaningful tag of some kind.$>$

REQ-1:	REQ-2:

\section{System Feature 2 (and so on)}


\chapter{Other Nonfunctional Requirements}

\section{Performance Requirements}
$<$If there are performance requirements for the product under various
circumstances, state them here and explain their rationale, to help the
developers understand the intent and make suitable design choices. Specify the
timing relationships for real time systems. Make such requirements as specific
as possible. You may need to state performance requirements for individual
functional requirements or features.$>$

The software shall run on an embedded system with 50KB RAM and a 550KB hard drive
Lag is unacceptable as it can result in collisions

\section{Safety Requirements}
$<$Specify those requirements that are concerned with possible loss, damage, or
harm that could result from the use of the product. Define any safeguards or
actions that must be taken, as well as actions that must be prevented. Refer to
any external policies or regulations that state safety issues that affect the
product’s design or use. Define any safety certifications that must be
satisfied.$>$

\section{Security Requirements}
$<$Specify any requirements regarding security or privacy issues surrounding use
of the product or protection of the data used or created by the product. Define
any user identity authentication requirements. Refer to any external policies or
regulations containing security issues that affect the product. Define any
security or privacy certifications that must be satisfied.$>$

\section{Software Quality Attributes}
$<$Specify any additional quality characteristics for the product that will be
important to either the customers or the developers. Some to consider are:
adaptability, availability, correctness, flexibility, interoperability,
maintainability, portability, reliability, reusability, robustness, testability,
and usability. Write these to be specific, quantitative, and verifiable when
possible. At the least, clarify the relative preferences for various attributes,
such as ease of use over ease of learning.$>$

\section{Business Rules}
$<$List any operating principles about the product, such as which individuals or
roles can perform which functions under specific circumstances. These are not
functional requirements in themselves, but they may imply certain functional
requirements to enforce the rules.$>$

\subsection{Background, Business opportunity, Customer needs}
The intersection is currently quite busy and unsafe for travelers. The system
should help with optimizing the flow of traffic through the intersection so that
travelers get to their destination safely. Priority should be given to vehicles
on Road 1, since that is the road with the most volume of vehicles passing
through the intersection. Road 3 is also a main road, and Road 2 should be given
the least priority. With the implementation of a traffic light control system,
the intersection should become much safer overall, and help decrease congestion
in the area.

\subsection{Business objectives and success criteria}
\begin{enumerate}
 \item BO-1: Implement a fully functional traffic light control system at the
       target intersection.
 \item BO-2: Implement a “night mode” which controls the intersection
       during specified night hours.
 \item BO-3: Implement an “emergency mode” which controls
       the intersection in case malfunctions occur in the control system.
 \item BO-4: A pedestrian light that turns green only when a button is pressed
       and is safe to do so.
 \item BO-5: Make sure the control system complies with local traffic laws.
 \item SC-1: Make sure the traffic flows well following initial release.
 \item SC-2: Decreased injuries after the system has been implemented.
\end{enumerate}

\subsection{Business risks}
\begin{enumerate}
 \item RI-1: The implementation of a traffic light control system might increase
       traffic flow through said intersection, causing unexpected congestion
       (Prob=0.5, Impact= 4)
 \item RI-2: The timing of the lights may not be synced with lights from close-by
       intersections, causing frustration in drivers (Prob=0.8, Impact=6)
 \item RI-3: Drivers ignoring traffic laws and cross red lights (Prob=0.000371,
       Impact=9)
 \item RI-4: Pedestrians ignoring pedestrian lights(Prob=0.1, Impact=9)
       
\end{enumerate}

\chapter{Other Requirements}
$<$Define any other requirements not covered elsewhere in the SRS. This might
include database requirements, internationalization requirements, legal
requirements, reuse objectives for the project, and so on. Add any new sections
that are pertinent to the project.$>$



\section{Appendix A: Glossary}
%see https://en.wikibooks.org/wiki/LaTeX/Glossary
$<$Define all the terms necessary to properly interpret the SRS, including
acronyms and abbreviations. You may wish to build a separate glossary that spans
multiple projects or the entire organization, and just include terms specific to
a single project in each SRS.$>$

\begin{enumerate}

 \item \textbf{TLMS} -
       \textbf{T}raffic
       \textbf{L}ight
       \textbf{M}onitoring
       \textbf{S}ystem
       
 \item \textbf{RB} -
       \textbf{R}eset
       \textbf{Button}
 \item \textbf{M} - Hardware malfunction: 1 indicates a malfunction, 0 for normal operation
 \item \textbf{1} - Light on Road 1
 \item \textbf{2} - Light on Road 2
 \item \textbf{3} - Light on Road 3
 \item \textbf{P1} - Pedestrian light on road 1
 \item \textbf{P2} - Pedestrian light on road 2
 \item \textbf{P3} - Pedestrian light on road 3
 \item \textbf{t1} - Timer for \textbf{1}
 \item \textbf{t2} - Secondary timer for everything else
 \item \textbf{G1} - Left turn signal on road 1
 \item \textbf{G3} - Left turn signal on road 3
 \item \textbf{S2} - Magnetic sensor which detects if a car/motorcycle is waiting on \textbf{2}\\
       Outputs: 1 if vehicle waiting, 0 otherwise
 \item \textbf{B3} - Button on road 3 which a pedestrian can hit to request to cross the intersection
 \item \textbf{BG} -
       \textbf{B}linking
       \textbf{G}reen
 \item \textbf{BR}
       \textbf{B}linking
       \textbf{R}ed
 \item \textbf{D} - \textbf{D}ay (6:00-20:00)
 \item \textbf{N} - \textbf{N}ight (20:00-6:00)
 \item \textbf{Clock} - Can have value \textbf{D} or \textbf{N}
\end{enumerate}

\section{Appendix B: Analysis Models}
$<$Optionally, include any pertinent analysis models, such as data flow
diagrams, class diagrams, state-transition diagrams, or entity-relationship
diagrams.$>$

\section{Appendix C: To Be Determined List}
$<$Collect a numbered list of the TBD (to be determined) references that remain
in the SRS so they can be tracked to closure.$>$

\end{document}
