%preamble
\documentclass[letterpaper]{article}
\synctex=1

\usepackage{geometry}
\usepackage{array}
\usepackage{lipsum}

\usepackage{graphicx}
\usepackage{float}
\graphicspath{ {images/} }

\usepackage{float}

\usepackage[hidelinks]{hyperref}

% \usepackage[section]{placeins}
%
% \newenvironment{changemargin}[2]{%
% \begin{list}{}{%
% \setlength{\topsep}{0pt}%
% \setlength{\leftmargin}{#1}%
% \setlength{\rightmargin}{#2}%
% \setlength{\listparindent}{\parindent}%
% \setlength{\itemindent}{\parindent}%
% \setlength{\parsep}{\parskip}%
% }%
% \item[]}{\end{list}}

% \usepackage{tabu}
%actual document
\begin{document}

%titlepage
\begin{titlepage}
 \begin{center}

  \LARGE
  ECE 321 Lab - Software Requirements Engineering
  
  Department of Electrical and Computer Engineering
  
  University of Alberta
  
  \vspace{2cm}
  
  Lab 2: Insert title
  
  \vspace{5cm}
  \Large
  
  \begin{tabular}{ | m{5cm} | m{5cm} | }
   \hline
   Student Name  & Student \\
   \hline
   Arun Woosaree & XXXXXX  \\
   \hline
   Max           & XXXXXX  \\
   \hline
   Liyao         & XXXXXX  \\
   \hline
  \end{tabular}
  
  
  % \begin{tabu} to 0.8\textwidth{  | X[c] | X[c] | }
  %   \hline
  %   Student Name & Student \\
  %   \hline
  %   Arun Woosaree & xxxxxxx \\
  %   \hline
  %   Navras Kamal & 1505463 \\
  %   \hline
  % \end{tabu}
  
  
 \end{center}
\end{titlepage}

%table of contents
% \tableofcontents
% \vfill
% \newpage

\section{Actual questions to ask:}
\begin{enumerate}
 \item How is the intersection currently being controlled?
 \item Why do we need a new system?
 \item what are the 5 most important features that should be implemented as soon as possible?
 \item if an emergency vehicle comes by, should they have the power to change the lights?
 \item any laws we need to be aware of that we must comply with?
 \item how might change in weather affect the implementation?
 \item how do we make sure that the lights here will sync with traffic flow
       coming from other nearby intersections?
 \item which direction is the dominant flow of traffic?
 \item how many accidents/ how frequent are accidents?\\
       what part of the intersection do they usually happen in?
 \item should we be able to update timings as time goes on?
       
 \item How busy is the intersection
 \item what time of day is there the most traffic?
       
 \item what's the ideal length of time to have a green/red light in each direction
 \item should the system be able to detect if a car is waiting for the light to change?
 \item photos/ catching people running red light
 \item should pedestrians be able to request a light change
 \item what length should the yellow light be
       
 \item how many lanes on each side?
 \item are any of the roads connecting to this intersection one way?
 \item are left turns required?\\
       should there be a dedicated light for left turns?\\
       dedicated turning lane?\\
       dual turning lane?\\
       ideal time for turns\\
 \item right turns\\
       dedicated turning lane? -- if so, do we need a system for pedestrians
       is it free flow?\\
       should right turns be controlled by lights?
 \item how often to pedestrians need to cross?\\
       where are pedestrians allowed to cross?\\
       can the pedestrians cross diagonally? (if there are a lot of pedestrians)
 \item bike lanes? how many bikes frequent the intersection?
       
       
       
       
 \item what are your nice-to-haves?
\end{enumerate}

\section{Stakeholders to consider}
\label{stakeholders}
\begin{enumerate}
 \item Customers
 \item End users
 \item Requirement alalysts
 \item Developers
 \item Testers
 \item Documentation writers
 \item Project managers
 \item Legal staff
 \item Manufacturers
\end{enumerate}

\section{Things we need:}
\begin{enumerate}
 \item description of functionality
 \item agreement on problem definition
 \item root causes - why do we need the system?
 \item who are the Stakeholders?  \ref{stakeholders}
 \item system boundary
 \item constraints
 \item keep in mind: needs vs features
\end{enumerate}

\section{Types of questions to ask:}
\begin{enumerate}
 \item why is this
 \item what else could
 \item what happens when
 \item why do you
 \item why don't you
 \item does anyone ever
 \item context-free questions
\end{enumerate}

\section{structure of the interview:}
\begin{enumerate}
 \item Establish the customer or user profile
 \item assess the problem
 \item understand the user enviroment
 \item recap at the end
 \item assess your solution
 \item assess the opportunity
 \item assess the reliability, performance, and support needs
 \item other Requirements
 \item wrap-up
 \item recap
\end{enumerate}



\section{general list of questions:}
\begin{enumerate}
 \item establishing the user profile:\\
       what are your key responsibilities\\
       what outputs do you produce or whom?\\
       when is the solution successful for you?\\
       what problems interfere with your success?\\
       what makes your job easier or more difficult?\\
       who are the users and what are their backgrounds?\\
       what platforms are in use now, and in the future?\\
       are there additional relevant applications?\\
       what are your expectations for training time?\\
       what kind of user help do you need? (manual, user support)
       
       
 \item Here's what we think the problem definition is:
       -------------------------------------------------------
       it will affect: ---------------------------------------
       which will result in ----------------------------------
       so the solution should have these features:------------
       which has these benefits: -----------------------------
       Do you have anything to add?
 \item What's the highest priority issue/root cause? \\
       for each problem: \\
       why does this problem exist?\\
       how do you solve it now?\\
       how would you rather solve it in the future?\\
       --- rank the other root causes ---
 \item -- stakeholders --
 \item Who are the users?\\
       Who is the customer/buyer of the system?\\
       Who will evaluate and who will maintain the system\\
       Anyone else?
 \item --system boundary --\\
       Who will operate it?\\
       who will supply, use, or remove information from the system\\
       where will the system be used?\\
       what other external systems will interact with this one?\\
 \item -- constraints --
       technical constrains\\
       economical\\
       political - any laws we should be aware of?\\
       system-imposed constraints -- compatible with existing systems? operating systems\\
       enviromental constraints\\
       security\\
 \item what resources are available?
\end{enumerate}

\section{Info:}
Client:
Alberta Traffic Supply Ltd.\\
7798 16 th Street\\
Edmonton, Alberta, T6P 1L9\\
Western Canada largest traffic sign manufacture and traffic control company\\




\end{document}
